Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-04 treestats_paper.tex
N -> Ne in \rho

\begin{figure}
    \centering
    \includegraphics{tskit_stat_benchmarks/benchmarks_without_copy_longer_genome.pdf}
    \caption{Comparison of time required to compute site statistics
        between matrix and tree based methods. For each sample size, a single replicate
        was obtained using \texttt{msprime} with scaled neutral mutation rate $\theta = 4N_e\mu$ and
        scaled recombination rate $\rho = 4Nr$ both equal to $10^4$. For each replicate, Tajima's $D$
        \citep{Tajima1989-de} statistic was calculated using \texttt{tskit}, \texttt{libsequence}
        \citep{Thornton2003-wj}, and \texttt{scikit-allel} \krt{need cite for this}.
        The solid green line shows the result of fitting the timing data to a model based on the expected complexity of the 
        algorithm used by \texttt{tskit}. \krt{need to revisit the correctness of this}
        \label{fig:stats_performance}
    }
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics{tskit_stat_benchmarks/benchmarks_without_copy_longer_genome.pdf}
    \caption{Comparison of time required to compute site statistics
        between matrix and tree based methods. For each sample size, a single replicate
        was obtained using \texttt{msprime} with scaled neutral mutation rate $\theta = 4N_e\mu$ and
        scaled recombination rate $\rho = 4N_er$ both equal to $10^4$. For each replicate, Tajima's $D$
        \citep{Tajima1989-de} statistic was calculated using \texttt{tskit}, \texttt{libsequence}
        \citep{Thornton2003-wj}, and \texttt{scikit-allel} \krt{need cite for this}.
        The solid green line shows the result of fitting the timing data to a model based on the expected complexity of the 
        algorithm used by \texttt{tskit}. \krt{need to revisit the correctness of this}
        \label{fig:stats_performance}
    }
\end{figure}
